Synthesizing Symmetric Lenses

### 2018-07-12 papers/SymmetricLenses/main.tex
fixed typo
mentioned tuning and interaction in the abstract

We describe an implementation of simple symmetric lenses and our synthesis
procedure as extensions to the Boomerang language~\cite{Boomerang}. We evaluate
its performance on 48 benchmark examples drawn from Flash Fill~\cite{flashfill},
Augeus~\cite{augeas2}, the bidirectional programming literature, and electronic
file format synchronization tasks. Our implementation can synthesize all these
lenses in under 30 seconds.
\end{abstract}

@@

In this evaluation, we aim to answer three primary questions:
\begin{enumerate}
\item Does the synthesis algorithm find the correct lens?
\item Is the synthesis procedure efficient enough to be used in everyday
  development?
\item How much slower is our tool on bijective lens synthesis benchmarks than
  the existing Optician system customized for bijective lenses?

>>>>

We describe an implementation of simple symmetric lenses and our synthesis
procedure as extensions to the Boomerang language~\cite{Boomerang}. We evaluate
its performance on 48 benchmark examples drawn from Flash Fill~\cite{flashfill},
Augeus~\cite{augeas2}, the bidirectional programming literature, and electronic
file format synchronization tasks. After modest tuning, which is encouraged by
the interactive nature of the tool, our implementation can synthesize all these
lenses in under 30 seconds.
\end{abstract}

@@

In this evaluation, we aim to answer four primary questions:
\begin{enumerate}
\item Does the synthesis algorithm find the correct lens?
\item Is the synthesis procedure efficient enough to be used in everyday
  development?
\item How much slower is our tool on bijective lens synthesis benchmarks than
  the existing Optician system customized for bijective lenses?
